---
title: "Babine Camera Project Summary"
author: "Kristen Peck"
date: "9 November, 2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=F)
source("reporting.R")
ls()
```

## Activity summary, Nov. 1 to 7, 2021 ##

DFO and LBN continue to run the Babine Fish Fence, which has remained fish tight since we switched to the camera extension project in early October. The numbers of both sockeye and coho are starting to trickle down, with an average of `r round(mean(unlist(table.end[(nrow(table.end)-7):nrow(table.end),2]),na.rm=T),0)` daily sockeye and `r round(mean(unlist(table.end[(nrow(table.end)-7):nrow(table.end),4]),na.rm=T),0)` daily coho over the last week. One of the cameras had a glitch so we closed that trap on the 6th until we can figure out the cause of the problem. We currently have three camera chutes running 24 hrs a day. Here is an updated summary of the counts up till a couple days ago:


```{r summary table, echo=FALSE, warnings=F}
library(knitr)
kable(table.end)
```

## Compare fish counts from cameras (traps 3-6) and manual traps (traps 1,2 and 7)

```{r figure cam vs man, echo=FALSE,warnings=F, fig.height=4, fig.width=6, fig.cap = "Daily total number of fish passing through the camera chutes (traps 3-6) versus the manual counting traps (traps 1,2 and 7)."}
plot.cam.vs.man2
```

## Daily counts for end of season

```{r end of season, echo=FALSE, warnings=F, fig.height=4, fig.width=6, fig.cap ="Daily counts of salmon. The vertical line marks the start of counting using the camera chutes."}
plot.daily.salmon.end
```

## Daily counts in context

```{r whole season, echo=FALSE, warnings=F, fig.height=4, fig.width=6, fig.cap ="Daily counts of salmon for the whole season of 2021. The vertical line marks the start of counting using the camera chutes."}
plot.daily.salmon
```

```{r coho whole season, echo=FALSE, warnings=F, fig.height=4, fig.width=6, fig.cap ="Daily counts of coho for the whole season of 2021. The vertical line marks the start of counting using the camera chutes."}
plot.daily.coho
```

## Cumulative counts

```{r cumulative whole season, echo=FALSE, warnings=F, fig.height=4, fig.width=6, fig.cap ="Cumulative counts of salmon for the whole season of 2021. The vertical line marks the start of counting using the camera chutes."}
plot.cumul.daily
```


```{r cumulative coho whole season, echo=FALSE, warnings=F, fig.height=4, fig.width=6, fig.cap ="Cumulative coho counts for the whole season of 2021. The vertical line marks the start of counting using the camera chutes."}
plot.cumul.daily.coho
```

**Note on Species Codes:**
CO = Coho; 
jk.CH = jack Chinook; 
jk.SK = jack Sockeye; 
lg.CH = large Chinook; 
lg.SK = large Sockeye; 
PK = Pink

