---
title: "Babine Camera Project Summary"
author: "Kristen Peck"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=F)
source("reporting.R")
ls()
```




## Temperature and Water Level

Water temperature peaked at `r max.wt.temp$temp` degrees Celsius on `r as_date(max.wt.temp.date$datetime)` and reached a low of `r min.wt.temp$temp`degrees Celsius on `r unique(as_date(min.wt.temp.date$datetime))`.

The water level varied from a maximum of `r maxmin.wt.flow$max`cms on  `r as_date(max.flow.date$date)`, and a minimum of `r maxmin.wt.flow$min`cms on  `r as_date(min.flow.date$date)`.

```{r temps, echo=FALSE, warnings=F, fig.height=4, fig.width=6, fig.cap ="Air and water temperature measured twice daily at the Babine fish fence from July 14th to Nov 25th, 2021."}
plot.temps
```

```{r waterlevels, echo=FALSE, warnings=F, fig.height=4, fig.width=6, fig.cap ="Water discharge at an Environment Canada hydrological station (08EC013) immediately downstream of the Babine fish fence from July 14th to Nov 25th, 2021. Shaded area is the standard deviation of the discharge from 2010 to 2020 for reference."}
plot.flow.ec
```

## Total counts

The total number of salmon counted through during the regular season and extension program are shown in *salmon table*.

```{r salmon table, echo=FALSE, warnings=F}
library(knitr)
kable(fish.totals.reg, caption = "Total salmon and non-salmon by species and size class counted through the fence during the regular season (July 14-Oct 1) and the season extension (Oct 2-Nov 25).")
```



## Daily counts for end of season


```{r end of season, echo=FALSE, warnings=F, fig.height=4, fig.width=6, fig.cap ="Daily counts of salmon. The vertical line marks the start of counting using the camera chutes."}
plot.daily.salmon.end
```

## Daily counts in context

```{r whole season, echo=FALSE, warnings=F, fig.height=4, fig.width=6, fig.cap ="Daily counts of salmon for the whole season of 2021. The vertical line marks the start of counting using the camera chutes."}
plot.daily.salmon
```

```{r coho whole season, echo=FALSE, warnings=F, fig.height=4, fig.width=6, fig.cap ="Daily counts of coho for the whole season of 2021. The vertical line marks the start of counting using the camera chutes."}
plot.daily.coho
```

## Cumulative counts

```{r cumulative whole season, echo=FALSE, warnings=F, fig.height=4, fig.width=6, fig.cap ="Cumulative counts of salmon for the whole season of 2021. The vertical line marks the start of counting using the camera chutes."}
plot.cumul.daily
```


```{r cumulative coho whole season, echo=FALSE, warnings=F, fig.height=4, fig.width=6, fig.cap ="Cumulative coho counts for the whole season of 2021. The vertical line marks the start of counting using the camera chutes."}
plot.cumul.daily.coho
```

```{r cam vs man, echo = F, warnings=F, fig.height=4, fig.width=6, fig.cap = "Daily total salmon counted through camera chutes versus manual counting chutes (corrected for number of open chutes)." }
plot.cam.vs.man3
```


```{r cam vs man jackSK, echo = F, warnings=F, fig.height=4, fig.width=6, fig.cap = "Proportion of jack sockeye out of total sockeye enumerated from video and from the live visual counts." }
plot.jackSK.rate
```


```{r fishbyhour, echo = F, warnings=F, fig.height=4, fig.width=6, fig.cap = "Mean fish per hour through the day and night, corrected for number of open chutes. Vertical orange and red lines represent the minimum and maximum nautical sunrise and sunset times, respectively, through the season extension (Oct-Nov)." }
plot.fishbyhour
```

```{r fishbydaynight, echo = F, warnings=F, fig.height=4, fig.width=6, fig.cap = "Total number of fish per chute passing through the camera chutes between sunrise and sunset (day) and sunset and sunrise (night)." }
plot.dayandnight
```



**Note on Species Codes:**
CO = Coho; 
jk.CH = jack Chinook; 
jk.SK = jack Sockeye; 
lg.CH = large Chinook; 
lg.SK = large Sockeye; 
PK = Pink;
ST = Steelhead

